A Method for Analysing Heterogeneous Population Data with 2D Detection Function Distance Sampling

### 2018-04-12 Draft.tex
4/12 session 1

\documentclass[11pt]{article}
\usepackage{multicol,graphicx,float,tikz,tikz-qtree,scrextend}
\usepackage[margin=1 in]{geometry}
\title{A Method for Analysing Heterogeneous Population Data Within the Two-Dimensional Detection Function Distance Sampling Framework, and its Associated Software}
\date{January 2018}
\author{Calliste Fagard-Jenkin}

@@

Distance sampling is a methodology within ecological statistics which allows us to produce unbiased estimates of animal population sizes even when the detection of any individual in the survey area is uncertain. First, a quick description of its simpler younger brother, strip sampling (in which detection of individuals is certain), will be given in order to illustrate the fundamental principles of greatest importance.

@@

\section{Algorithms and Implementation}
\subsection{Understanding the LT2D software, and its architecture}
In order to implement covariate inclusion it is vital to first understand the inner workings of the LT2D package, so that we may ascertain both the complexity of the task at hand, and also the most efficient method with which to proceed. A simplification of the software's top-level fitting function call hierarchy (as of August 2017, before the project began), which retains the features of greatest importance and relevance is illustrated by figure 4.

@@

\subsection{Covariate Inclusion into the Likelihood}
\subsection{Covariate Inclusion into Abundance Estimation}
\subsection{Modification of Goodness of Fit Functions}
\subsection{Modification of Plot Functions}
\subsection{Implementation of the Bootstrap}

\section{Case Studies}
\subsection{Batang Toru}
\subsection{Jantho}

\section{Statistical Consultancy and Software Feedback}

>>>>

\documentclass[11pt]{article}
\usepackage{multicol,graphicx,float,tikz,tikz-qtree,scrextend}
\usepackage[margin=1 in]{geometry}
\title{A Method for Analysing Heterogeneous Population Data with 2D Detection Function Distance Sampling}
\date{January 2018}
\author{Calliste Fagard-Jenkin}

@@

Distance sampling is a methodology within ecological statistics which allows us to produce unbiased estimates of animal population sizes even when the detection of any individual in the survey area is uncertain. First, a quick description of its simpler alternative, strip sampling (in which detection of individuals is certain), will be given in order to illustrate the fundamental principles of greatest importance.

@@

\section{Algorithms and Implementation}
\subsection{Covariates; why include them, and how?}
\subsection{Understanding the LT2D software and its architecture}
In order to implement covariate inclusion it is vital to first understand the inner workings of the LT2D package, so that we may ascertain both the complexity of the task at hand, and also the most efficient method with which to proceed. A simplification of the software's top-level fitting function call hierarchy (as of August 2017, before the project began), which retains the features of greatest importance and relevance is illustrated by figure 4.

@@

\subsection{Covariate Inclusion into the Likelihood}
\subsection{Covariate Inclusion into Abundance Estimation}
\subsection{Modification of Goodness of Fit Functions}
\subsection{Modification of Plot Functions}
\subsection{Covariate implementation}
\section{Usage of the new sofware}
\subsection{Model specification for the user}
\subsection{Simulation studies}

\section{Going forwards}
\subsection{Additional desired features}
\subsection{A proposed approach for mixture model incorporation}
